BSOS

### 2014-06-08 Paper.tex
added more background

\part{Fundamental Theory of Operating Systems}

\begin{lstlisting}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU’s operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

                Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program – hence the name, “interrupt”. The kernel handles interrupts.

                Three different types of interrupts are hardware interrupts, software interrupts, and traps. Hardware interrupts may come from a key on a keyboard being hit or the click of a mouse. Software interrupts are generated by programs. Traps come from the CPU itself due to errors or conditions which require the OS for assistance.

                When a computer initially turns on, it runs in supervisor mode. The first programs to run have unlimited access to hardware. When the OS allows another program to take control, the computer transitions into protected mode, where programs’ access to the CPU’s set of instructions is limited. To leave protected mode, an interrupt has to be triggered so that way the kernel will be able to take charge once again.

                An OS manages the interactions between hardware and software on the computer. The most common Operating Systems are Microsoft Windows, Mac OS X, and Linux.
\end{lstlisting}

\part{Booting Up}
BSOS's bootstrapping process can be classified by architecture.

@@

\paragraph{ARM}
On ARM-based machines, specifically those with Cortex-M3 processors, the bootstrapping process [...]

@@

>>>>

\part{Booting Up}
BSOS, as a portable and abstracted system, must be capable of bootstrapping on a variety of diverse and divergent architectures. Although hundreds exist, ranging from giants like x86, POWER, and ARM to lesser known embedded architectures like AVR and MIPS, the vast majority of fall into one of two families: CISC and RISC.

CISC, or Complex Instruction Set Computing, began as a side effect of early computer development. As the (comparatively primitive) computers and calculators of the 1950s and 1960s became increasingly complex and multifunctional, they required new paradigms and methods of automation. Because languages like FORTRAN and ALGOL required a certain amount of boilerplate in order to operate, early system architects build complex control structures into the instruction sets of their machines, bridging the semantic gap between microcode-assembly and full-features programming languages.

@@

\paragraph{ARM}
On ARM-based machines, specifically those with Cortex-M3 processors, the bootstrapping process is remarkably similar. Despite the RISC (Reduced Instruction Set Computing) nature of the ARM architecture

@@

\part{Running the OS}

\begin{lstlisting}
Reyna's stuff goes here.
\end{lstlisting}
